Approximation as Differentiation

### 2025-04-01 notes/sec/cmon-enriched.tex
biadditive -> bilinear seems more common.
$\CMon569XZilmsenriched presheaf.

\subsubsection{$\CMon$-enriched categories}

We note that if a category $C$ is $\CMon$-enriched, then:
\begin{enumerate}
\item Every hom-object $\Hom{C}{A}{B}$ is a commutative monoid of morphisms; we write $\zero_{A,B}$ (zero
morphism) for the unit, and $+_{A,B}$ (addition of morphisms) for the binary operation.
\item Composition is \emph{biadditive}, i.e.~given by a family of morphisms $\Hom{C}{B}{C} \tensor
\Hom{C}{A}{B} \to \Hom{C}{A}{C}$ in $\CMon$ that preserve the additive structure in $\Hom{C}{B}{C}$ and
$\Hom{C}{A}{B}$ separately:

@@

>>>>

\subsubsection{$\CMon$-enriched category}

We note that if a category $C$ is $\CMon$-enriched, then:
\begin{enumerate}
\item Every hom-object $\Hom{C}{A}{B}$ is a commutative monoid of morphisms; we write $\zero_{A,B}$ (zero
morphism) for the unit, and $+_{A,B}$ (addition of morphisms) for the binary operation.
\item Composition is \emph{bilinear}, i.e.~given by a family of morphisms $\Hom{C}{B}{C} \tensor
\Hom{C}{A}{B} \to \Hom{C}{A}{C}$ in $\CMon$ that preserve the additive structure in $\Hom{C}{B}{C}$ and
$\Hom{C}{A}{B}$ separately:

@@

\subsubsection{$\CMon$-enriched presheaf}

For any monoidal category $V$ and $V$-enriched categories $C$ and $D$, the action of a \emph{$V$-enriched}
functor $F: C \to D$ on morphisms takes the form of a morphism $C(X,Y) \to D(F(X),F(Y))$ between hom-objects
in $V$. In the specific setting of a $\CMon$-enriched presheaf $F: C^\op \to \CMon$, we have that $F$
satisfies:
\begin{itemize}
\item $F(0_{X,Y}) = 0_{FY,FX}$
\item $F(f + g) = Ff + Fg$
\end{itemize}
